\textsf{Are large language models superhuman chemists?}

### 2024-10-27 src/tex/appendix.tex
try to make compile work

To better understand the cognitive demands of chemical assessment, we categorized the questions in the ChemBench corpus according to the primary skills required to solve them. The table \Cref{tab:chembench_corpus_models_failed_cognitive} below shows representative examples of questions that state-of-the-art models failed to answer correctly across different cognitive skill categories, including knowledge, reasoning and intuition.
\begin{table}
    \centering
    \small
    \caption{\textbf{Examples of required skills evaluated in the \chembench corpus that the state-of-the-art model failed to answer correctly} The table displays the number of questions for each skill, along with an example question that the model failed to answer.}
    \label{tab:chembench_corpus_models_failed_cognitive}
    {\fontsize{8}{9}\selectfont
        \begin{tabularx}{\textwidth}{X}
            \toprule
            \multicolumn{1}{c}{\textbf{Knowledge} 919 Questions} \\
            \midrule
            Which of the following are true for phosphoric acid? \\
            A. Is a weak acid, so it is not toxic \\
            B. Should never be tasted \\
            C. Though a component of soft drinks, reacts vigorously with water when in concentrated form \\
            \midrule
            \multicolumn{1}{c}{\textbf{Reasoning} 987 Questions} \\
            \midrule
            Which of the following elements has the largest atomic radius? \\
            A. \ce{Fr} \\
            B. \ce{He} \\
            C. \ce{Li} \\
            D. \ce{Rb} \\
            \midrule
            \multicolumn{1}{c}{\textbf{Intuition} 1001 Questions} \\
            \midrule
            Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
            A. [START_SMILES]CCc1c(CCOC)nn(-c2ccccc2)c1-c1ccccc1[END_SMILES] \\
            B. [START_SMILES]Cc1cc(/C=C2\\C(=N)N3N=C(S(C)(=O)=O)SC3=NC2=O)c(C)n1Cc1ccccc1[END_SMILES] \\
            \midrule
            \multicolumn{1}{c}{\textbf{Calculation} 128 Questions} \\
            \midrule
            The cell potential for the overall cell reaction during electrolysis of water, \ce{2H2O(l) -> 2H2(g) + O2(g)} is \SI{-1.23 V}. What is the standard electrode potential for the half reaction, \ce{2H2O(l) -> O2(g) + 4H+(aq) + 4e-} in V? \\
            \bottomrule
        \end{tabularx}
    }
\end{table}

>>>>

To better understand the cognitive demands of chemical assessment, we categorized the questions in the ChemBench corpus according to the primary skills required to solve them. The table \Cref{tab:chembench_corpus_models_failed_cognitive} below shows representative examples of questions that state-of-the-art models failed to answer correctly across different cognitive skill categories, including knowledge, reasoning and intuition.
\begin{table}
    \centering
    \small
    \caption{\textbf{Examples of required skills evaluated in the \chembench corpus that the state-of-the-art model failed to answer correctly} The table displays the number of questions for each skill, along with an example question that the model failed to answer.}
    \label{tab:chembench_corpus_models_failed_cognitive}
    {\fontsize{8}{9}\selectfont
        \begin{tabularx}{\textwidth}{X}
            \toprule
            \multicolumn{1}{c}{\textbf{Knowledge} 919 Questions} \\
            \midrule
            Which of the following are true for phosphoric acid? \\
            A. Is a weak acid, so it is not toxic \\
            B. Should never be tasted \\
            C. Though a component of soft drinks, reacts vigorously with water when in concentrated form \\
            \midrule
            \multicolumn{1}{c}{\textbf{Reasoning} 987 Questions} \\
            \midrule
            Which of the following elements has the largest atomic radius? \\
            A. \ce{Fr} \\
            B. \ce{He} \\
            C. \ce{Li} \\
            D. \ce{Rb} \\
            \midrule
            \multicolumn{1}{c}{\textbf{Intuition} 1001 Questions} \\
            \midrule
            Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
            A. [START\_SMILES]CCc1c(CCOC)nn(-c2ccccc2)c1-c1ccccc1[END\_SMILES] \\
            B. [START\_SMILES]Cc1cc(/C=C2\\C(=N)N3N=C(S(C)(=O)=O)SC3=NC2=O)c(C)n1Cc1ccccc1[END\_SMILES] \\
            \midrule
            \multicolumn{1}{c}{\textbf{Calculation} 128 Questions} \\
            \midrule
            The cell potential for the overall cell reaction during electrolysis of water, \ce{2H2O(l) -> 2H2(g) + O2(g)} is \SI{-1.23}{V}. What is the standard electrode potential for the half reaction, \ce{2H2O(l) -> O2(g) + 4H+(aq) + 4e-} in V? \\
            \bottomrule
        \end{tabularx}
    }
\end{table}
